---
title       : Product Statistics
subtitle    : A course project on the Developing Data Products course
author      : Viacheslav Shybaiev
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
```{r init,  echo=FALSE, include=FALSE}
source("../shiny-app/osp.R")
subsites=load_subsite_names()
```

## Product Statistics Overview
# Introduction

This data product is aimed to provide product usage indicators of a mobile
application.

The data product is created with Shiny framework of the RStudio and allows users
to access data using a web browser from any location.

Tracking the mobile app usage indicatiors is a viable process after the
mobile appplication is launched for public availability.

For the purpose of the course project the real application name and the data was obfuscated
and cached from the database.

Following slides highlight examples of the main interactive reports available with the
shiny app.

---

## Product Usage Indicators - Installs
Example of the Installs report. With the shiny app user can interact by selecting
required number of months to include into the diagram.
```{r  echo=TRUE, include=TRUE, results='markup', fig.height=4}
downloads=kpi_monthly_downloads (-1, 0, plot=TRUE, 1:6)
```

---
## Product Usage Indicators - Position
Position analysis provides information about the product placement in the app stores.
With the app user can select countries and platforms to get the report for.
```{r   echo=TRUE, include=TRUE, results='markup', fig.height=5}
mydata = positions_analysis(285, 6) 
```

---
## Product Usage Indicators - Cohort Analysis
Cohort analysis provides information about the buckets of users of the product with 
different start date when they first tried the product. This report can help to analyse
the number of times of product usage month over month.

With the app user can select countries and platforms to get the report for.
```{r   echo=TRUE, include=TRUE, results='markup', fig.height=3}
mydata = cohort_analysis (315,3)
```



